### 2019-09-09 experiments.tex
little more info
response, final touches

In order to evaluate our approach and implementation, we applied
nondeterminism detection to real Python code, including some widely
used libraries (according to GitHub, {\tt pyfakefs} is used by at least
338 other projects, and {\tt redis-py} is used by at least 50,000).  The primary
points we wanted to explore were {\bf RQ1:} whether our approach was able to reliably detect actual
nondeterminism, {\bf RQ2:} whether the overhead of nondeterminism
detection for real systems was acceptable, and {\bf RQ3:} whether the performance of
delta-debugging in this setting was acceptable, in terms of both time
and results (amount of reduction in test size).  We chose two of
the subjects, {\tt redis-py} and {\tt pyfakefs}, based on the fact that they were previously-existing large
examples of TSTL harnesses, and therefore serve to show how easily our
approach can be integrated into an existing large-scale test
generation effort.  The other two subjects were chosen, and new harnesses
written, specifically to demonstrate specific, important sources of
nondeterminism in Python code: concurrency and hash salting.

@@

\begin{table}
\centering
\begin{tabular}{l|l|r|r|l}
Subject & Detection & Overhead & Reduction & Reduction time \\
\hline
Parallel Sort & Yes (see below) & $\sim$40\% & $\sim$85\% & $\sim$2 minutes\\
{\tt redis-py} & Yes (see below) & $\sim$20\% & $\sim$95\% & $\sim$10 minutes\\
{\tt datarray} & Yes (see below) & $\sim$93\% & $\sim$90\% & $\sim$92
  seconds\\
{\tt pyfakefs} & Yes (see below) & $\sim$8\% & $\sim$99\% & $\sim$1 second  \\
\end{tabular}
\caption{Overview of experimental results}
\label{tab:overviewexp}
\end{table}

>>>>

In order to evaluate our approach and implementation, we applied
nondeterminism detection to real Python code, including some widely
used libraries (according to GitHub, {\tt pyfakefs} is used by at least
338 other projects, and {\tt redis-py} is used by at least 50,000).  The primary
points we wanted to explore were {\bf RQ1:} whether our approach was able to reliably detect actual
nondeterminism, {\bf RQ2:} whether the overhead of nondeterminism
detection for real systems was acceptable, and {\bf RQ3:} whether the performance of
delta-debugging in this setting was acceptable, in terms of both time
and results (amount of reduction in test size).  We chose two of
the subjects, {\tt redis-py} and {\tt pyfakefs}, based on the fact that they were previously-existing large
examples of TSTL harnesses, and therefore serve to show how easily our
approach can be integrated into an existing large-scale test
generation effort.  The other two subjects were chosen, and new harnesses
written, specifically to demonstrate specific, important sources of
nondeterminism in Python code: concurrency and hash salting.  In
addition to our core research questions ({\bf RQ1-RQ3}) shared by all subjects, we
report on particular aspects of using the TSTL nondeterminism tools
specific to each subject.

@@

\begin{table}
\centering
\begin{tabular}{l|l|r|r|l}
& \multicolumn{1}{c}{\bf RQ1} & \multicolumn{1}{|c|}{\bf RQ2} &
                                                              \multicolumn{2}{c}{\bf RQ3}\\
  \hline
Subject & Detection & Overhead & Reduction \%
                                                        & Reduction time\\
\hline
Parallel Sort & Yes (see below) & $\sim$40\% & $\sim$85\% & $\sim$2 minutes\\
{\tt redis-py} & Yes (see below) & $\sim$20\% & $\sim$95\% & $\sim$10 minutes\\
{\tt datarray} & Yes (see below) & $\sim$93\% & $\sim$90\% & $\sim$92
  seconds\\
{\tt pyfakefs} & Yes (see below) & $\sim$8\% & $\sim$99\% & $\sim$1 second  \\
\end{tabular}
\caption{Overview of experimental results}
\label{tab:overviewexp}
\end{table}

### 2019-09-09 implementation.tex
missing paren
response, final touches

The implementation of the above ideas is conceptually straightforward,
and should be easy to apply in other automated test generation
settings with a natural notion of actions.  We present out
implementation by first sketching a mapping from the formalism to one
particular popular way to represent automatically generated unit
tests, in Section \ref{sec:pools}.  The particular implementations of
horizontal (Section \ref{sec:horizimp} and vertical (Section
\ref{sec:vertimp}) determinism checks, as well as probabilistic
delta-debugging support (Section \ref{sec:ddimp}) are described after a general
overview of the TSTL testing tool (Section \ref{sec:tstlintro}).

@@

\caption{TSTL Method Calls for Nondeterminism Detection}
\label{tab:methods}
\begin{tabular}{l|p{8cm}}
%\hline
Name & Purpose \\
\hline
\hline
{\tt nondeterministic} & returns True if test exhibits final state nondeterminism in $k$
  tries with delay $d$, optionally only over pools in $\mathcal{P}$\\
\hline
{\tt stepNondeterministic} & as above, except checks all visible values
                       (compares state at every step)\\
\hline
{\tt processNondeterministic} & as above, except runs test provided in
                          subprocess and compares non-opaque output
                          values \\
\hline
{\tt P} & returns probability that a predicate holds for a test (with
          optional number of sample to use in estimate) \\
\hline
{\tt forceP} & wraps a predicate for test reduction, checking that it
               has desired probability of holding, using
         sample size and replications parameters \\
\hline
\hline

@@

>>>>

The implementation of the above ideas is conceptually straightforward,
and should be easy to apply in other automated test generation
settings with a natural notion of actions.  We present our
implementation by first sketching a mapping from the formalism to one
particular popular way to represent automatically generated unit
tests, in Section \ref{sec:pools}.  The particular implementations of
horizontal (Section \ref{sec:horizimp}) and vertical (Section
\ref{sec:vertimp}) determinism checks, as well as probabilistic
delta-debugging support (Section \ref{sec:ddimp}) are described after a general
overview of the TSTL testing tool (Section \ref{sec:tstlintro}).

@@

\caption{TSTL Method Calls for Nondeterminism Detection}
\label{tab:methods}
\begin{tabular}{l|p{8cm}}
%\hline
Name & Purpose \\
\hline
\hline
{\tt nondeterministic} & returns True if test exhibits final state nondeterminism in $k$
  tries with delay $d$, optionally only over pools in $\mathcal{P}$\\
\hline
{\tt stepNondeterministic} & as above, except checks all visible values
                       (compares state at every step)\\
\hline
{\tt processNondeterministic} & as above, except runs test provided in
                          subprocess and compares non-opaque output
                          values \\
\hline
{\tt P} & returns probability that a predicate holds for a test (with
          optional number of samples to use in estimate) \\
\hline
{\tt forceP} & wraps a predicate for test reduction, checking that it
               has desired probability of holding, using
         sample size and replications parameters \\
\hline
\hline

@@

\subsection{Key Challenges}
The key challenge in all of these implementations was choosing
appropriate default values.  In particular, how many times to retry
tests (horizontal determinism) or actions (vertical/failure determinism), what delays to use, and numbers of replications
required in nondeterministic delta-debugging.  Because our confidence
that these defaults are ideal is low, we made it easy to change the
values used, as shown by the presence of command line options and
optional function parameters in Tables \ref{tab:methods} and \ref{tab:options}.
